Elephant Seal Age JAE Intraspecific Variation

### 2023-12-08 paper/paperv3.qmd
Getting the p value for quadratic pup sex model

### H3a: Changes in pup sex ratio with increased maternal age

@@

@@

### H3b: Changes to annual cycle timing with increased maternal age

@@

pupsex_mod_summary <- summary(pup_sex_mod)
pupsex_mod_summary$coefficients %>% 
  as_tibble() %>% 
  mutate(Parameter = c("Intercept", "Age (linear)"),
         across(c(Estimate, `Std. Error`, `z value`), 
                \(x) format_signif(x, digits = 3)),
         `p value` = format_pval(`Pr(>|z|)`/2, digits = 3)) %>%
  select(-`Pr(>|z|)`) %>% 
  relocate(Parameter) %>% 
  knitr::kable()

@@

>>>>

### H3: Changes in pup sex ratio with increased maternal age

@@

pup_sex_quad <- glmer(
  is_male ~ poly(age10, 2, raw = TRUE) + (1 | animalID) + (1 | year),
  data = pup_sex_data, 
  family = "binomial"
  )

@@

### H4: Changes to annual cycle timing with increased maternal age

@@

pupsex_mod_summary <- summary(pup_sex_mod)
pupsex_quad_summary <- summary(pup_sex_quad)
pupsex_mod_summary$coefficients %>% 
  as_tibble() %>% 
  mutate(Parameter = c("Intercept", "Age (linear)"),
         across(c(Estimate, `Std. Error`, `z value`), 
                \(x) format_signif(x, digits = 3)),
         `p value` = format_pval(`Pr(>|z|)`/2, digits = 3)) %>%
  select(-`Pr(>|z|)`) %>% 
  relocate(Parameter) %>% 
  knitr::kable()

@@

```{r}
#| fig-width: 8
